Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-08 paper/main.tex
Updates

Figure~\ref{fig:intro} highlights some of these issues. To assist researchers
in constructing DAGs manually, we propose an iterative model construction
method that combines domain knowledge with data-driven insights. Our approach 
iteratively identifies pairs of variables with a missing edge in the DAG and

>>>>

Figure~\ref{fig:intro} highlights some of these issues. To assist researchers
in constructing DAGs manually, we propose an iterative model construction
method that combines domain knowledge with data-driven insights. Our approach
utilizes conditional independence testing to identify pair of variables in the
DAG that are missing an edge or have a superfluous edge. Based on this
information, in each iteration we present one such pair of variables to an
expert who then decides the orientation of the edge between the variables based
on their domain knowledge. The method also iteratively prunes all superfluous
edges in each iteration. As a result this approach guides the expert in
constructing their model while ensuring that the model is consistent with the
data.
